Implementing simplified INLA into `aghq`

### 2022-10-26 src/dev_sinla/sinla.Rmd
Finish bug fix, get .pdf rendering #16

```{r}
mm <- h$env$last.par
mean <- mm[h$env$random]
Q <- h$env$spHess(mm, random = TRUE)
Sigma <- solve(Q)

gaussian_df <- lapply(1:dat$n, function(i) {
  x <- seq(-5, 5, length.out = 1000)
  mean_i <- as.numeric(mean[i])
  sd_i <- as.numeric(sqrt(Sigma[i, i]))
  data.frame(index = i, x = x, pdf = dnorm(x, mean = mean_i, sd = sd_i))
}) %>%
  bind_rows()

samples_gaussian <- lapply(1:dat$n, function(i) {
  mean_i <- as.numeric(mean[i])
  sd_i <- as.numeric(sqrt(Sigma[i, i]))
  samples <- rnorm(M, mean_i, sd_i)
  data.frame("value" = samples)
}) %>%
  bind_rows(.id = "index")
```

>>>>

```{r}
x_Sigma <- solve(x_Q)

gaussian_df <- lapply(1:dat$n, function(i) {
  x <- seq(-5, 5, length.out = 1000)
  mean_i <- as.numeric(x_mean[i])
  sd_i <- as.numeric(sqrt(x_Sigma[i, i]))
  data.frame(index = i, x = x, pdf = dnorm(x, mean = mean_i, sd = sd_i))
}) %>%
  bind_rows()

samples_gaussian <- lapply(1:dat$n, function(i) {
  mean_i <- as.numeric(x_mean[i])
  sd_i <- as.numeric(sqrt(x_Sigma[i, i]))
  samples <- rnorm(M, mean_i, sd_i)
  data.frame("value" = samples)
}) %>%
  bind_rows(.id = "index")
```
